\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
pass on selection criteria

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of reproducible bugs from \tname.}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
  \\ \bottomrule
\end{tabular}
\end{table}

@@

\subsection{Selection Criterion}
\label{sec:selection-criterion}

@@

Amongst many DL libraries, the most popular libraries for developing AI-enabled applications and used in testing tools are \torch~and \tf. \jax~is a relatively newer entry to the list of libraries but it is rapidly gaining popularity as well. All three of these libraries are open source with active communities that support the libraries, making them very suitable for developing testing tools around. We chose these three popular datasets in order to enhance the process of developing testing tools around these libraries.

@@

For the bugs from these libraries, we focused on bug reports that have been accepted by the developer community as true bugs. We determine this by checking whether the bugs have appropriate labels and have been fixed with pull requests linked to them. Among these confirmed bug reports, we choose the ones that have enough information to reproduce the bugs i.e. code to reproduce the bug, enviroment required for reproduction, clear description of desired behavior etc. Once we can successfully reproduce the bug by creating the enviroment detailed in the report, we choose the bug to be included in our dataset.

>>>>

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of
    reproducible bugs from \tname.\Fix{Is this up to date? I have seen
  lots of activity recently but these numbers remain the same.}}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
  \\ \bottomrule
\end{tabular}
\end{table}

@@

\subsection{Selection Criteria}
\label{sec:selection-criterion}

@@

\textbf{Libraries.}~\torch~and \tf are popular DL libraries
intensively used in the literature. \jax\ is a newer library that has
been rapidly gaining popularity. All these libraries are open source
with active communities supporting their maintenaance.

%% We chose these three popular datasets in order to enhance the process
%% of developing testing tools around these libraries.

@@

\textbf{Bugs.}~We focused on bug reports that have been accepted by
the developer community as true bugs. We determine this by checking
whether the bugs have appropriate labels and have been fixed with pull
requests linked to them. Among these confirmed bug reports, we choose
the ones that have enough information to reproduce the bugs, i.e.,
code to reproduce the bug, enviroment required for
reproduction\Fix{Abid, can you confirm that environment here is not
  the same as venv-docker that we are using on Table 1? instead it
  means the version of CUDA, libraries, etc.? If so, avoid using the
  word environment.}, clear description of the desired behavior,
etc. Once we can successfully reproduce the bug by creating the
enviroment detailed in the report, we choose the bug to be included in
our dataset.
